---
title: "Lumo: a clean Quarto template for stunning data reports"
subtitle: "This document showcases how a Quarto report made using the <code>Lumo</code> format looks like. It also demoes a few tips and tricks I 💜"
format:
  lumo-html: 
    logo: "logo.png"                                     # Optional. Path to a logo displayed above the title
    github-repo: "https://github.com/holtzy/lumo"        # Optional. Adds a github corner at the top right
    primary-color: "#69b3a2"
    self-contained: true
    is-particlejs-enabled: true                          # Optional: display interactive particles in the document header
    bg-image: ""                                         # Optional: link to an image for the header background
author: Holtz Yan
date: last-modified
---




## Introduction

Quarto is probably my favorite tool in the R/Python universe. Transforming your code and thoughts into a stunning report in one click always blows my mind.

While the default Quarto appearance **looks great**, there are [a few tweaks](https://www.productive-r-workflow.com/quarto-tricks) I always apply to elevate the report even further. Rather than manually adding them each time, I bundled everything into a custom format called `lumo`.

```{r, warning=F, message=F, echo=FALSE}
library(tidyverse) 
library(hrbrthemes) # <1>
library(viridis) # <2>
library(ggiraph)
library(patchwork) 
library(sf)
```


::: {.column-margin}

Btw, you can learn how to master Quarto thanks to my online course: [Productive R Workflow](https://www.productive-r-workflow.com)

:::

```{ojs}
//| echo: false

// Define options for HTML files
viewof selectedFile = Inputs.select(
  [
    { value: "urgent.html", label: "Urgent" },
    { value: "ctas_month_waffle.html", label: "CTAS Month Waffle" }
  ],
  {
    label: "Select HTML file",
    value: "urgent.html",
    format: x => x.label
  }
)

// Base path for HTML files
basePath = "interactive/"

// Construct full path
fullPath = basePath + selectedFile.value

// Create and return the iframe element
html`<iframe src="${fullPath}" width="100%" height="500px" style="border:none;"></iframe>`
```


## Patient Visit Flow
<iframe src="interactive/patients_traffic.html" 
        width="100%" 
        height="100vh" 
        frameborder="0" 
        scrolling="no" 
        style="overflow: hidden;">
    Your browser does not support iframes.
</iframe>


This document aims at showcasing how a quarto document made with the `lumo` format looks like.



## ER Time Series

I strongly advise to create a dataviz theme that fits your company's brand. Here is one:



And now let's use it on a graph:




## Patient Traffic

For a complete list of features, [visit the documentation](https://www.productive-r-workflow.com/r/bonus/lumo-quarto-template)!

Oh and since we're here, did you know you can easily include a full width interactive map with `leaflet` in a quarto doc? 😍
```{r}
#| column: screen
#| out-width: 100%

knitr::include_url({"interactive/patients_traffic.html"})

```



## Documentation

The documentation for this quarto custom format is available [here](https://www.productive-r-workflow.com/r/bonus/lumo-quarto-template)


